Quality Definitions of Qualities

### 2020-06-11 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Minor notes added to quality definition document related to reproducibility

@@

>>>>

The importance of reproducibility is seen by retractions of influential papers,
like the review of
\href{https://www.theguardian.com/commentisfree/2020/jun/05/lancet-had-to-do-one-of-the-biggest-retractions-in-modern-history-how-could-this-happen}
{hydroxychloroquine trials}

@@

\wss{Reproducibility literature review is given in \citet{FeinbergEtAl2020}.
  Includes examples where replicability was found to be lacking.  Has a good
  litereature review in Section 2.}
